---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# medrxivr

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<br>
[![Travis build status](https://travis-ci.com/mcguinlu/medrxivr.svg?branch=master)](https://travis-ci.com/mcguinlu/medrxivr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/medrxivr?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/medrxivr)
[![Codecov test coverage](https://codecov.io/gh/mcguinlu/medrxivr/branch/master/graph/badge.svg)](https://codecov.io/gh/mcguinlu/medrxivr?branch=master)
<!-- badges: end -->

The goal of `medrxivr` is to provide programmatic access to the _medRxiv_ preprint repository.

## Installation

You can install the development version of this package using:


``` {r, eval = FALSE}
devtools::install_github("mcguinlu/medrxivr")
library(medrxivr)
```

## Example

To get the entire _medRxiv_ dataset to play around with, use the following command:

``` {r, eval=FALSE}

mx_results <- mx_search("*")

```

For a simple search strategy:

``` {r, eval=FALSE}

mx_results <- mx_search("dementia")

```

To find records that contain one of many keywords:

``` {r, eval=FALSE}

myquery <- c("dementia","vascular","alzheimer's") # Combined with OR

mx_results <- mx_search(myquery)

```

To combine different topic domains (currently, you can have up to 5 topics):

``` {r, eval=FALSE}

topic1  <- c("dementia","vascular","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins","cholesterol")     # Combined with OR
myquery <- list(topic1, topic2)                    # Combined with AND

mx_results <- mx_search(myquery)

```

## Download PDFs

Pass the results of your search above to the `mx_download()` function to download a copy of the PDF for each record. Note: PDFs are saved using the value of the `node` column in the dataset, which serves as a unique identifier for each record.

```{r, eval = FALSE}

mx_download(mx_results,     # Object returned by mx_search
            "pdf/",         # Directory to save PDFs to 
            create = TRUE)  # Create the directory if it doesn't exist

```

## Code of conduct

Please note that the `medrxivr` project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

