---
title: "Get started"
author: "Luke A McGuinness"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: yes
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{medrxivr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=FALSE, message=FALSE,warning=FALSE}
# Delete when done
library(medrxivr)
library(dplyr)
```

## Perform a simple search

``` {r, eval=FALSE}
library(medrxivr)

results <- mx_search("dementia")

```

## Dataset description

The dataset (in this case, `results`) returned by the search function above contains 10 variables: 

```{r, echo = FALSE}

mx_variables <-
  data.frame(
    Variable = c(
         "ID"      ,
         "title"   ,
         "abstract",
         "authors" ,
         "date"    ,
         "category",
         "doi"     ,
         "version" ,
         "author_corresponding",
         "author_corresponding_institution",
         "link_page",
         "link_pdf" ,
         "license"  ,
         "published"
    ),
    Description = c(
      "Unique identifier",
      "Preprint title",
      "Preprint abstract",
      "Author list in the format 'LastName, InitalOfFirstName.' (e.g. McGuinness, L.). Authors are seperated by a semi-colon.",
      "Date the preprint was posted, in the format YYYYMMDD.",
      "On submission, medRxiv asks authors to classify their preprint into one of a set number of subject categories.",
      "Preprint Digital Object Identifier.",
      "Preprint version number. As authors can update their preprint at any time, this indicates which version of a given preprint the record refers to.", 
      "Corresponding authors name.",
      "Corresponding author's institution.",
      "Link to preprint webpage. The \"?versioned=TRUE\" is required, as otherwise, the URL will resolve to the most recent version of the article (assuming there is >1 version available).",
      "Link to preprint PDF. This is used by `mx_download()` to download a copy of the PDF for that preprint.",
      "Preprint license",
      "If the preprint was subsequently published in a peer-reviewed journal, this variable contains the DOI of the published version."
    )
  )


knitr::kable(mx_variables, format = "html") %>%
  kableExtra::kable_styling(full_width = F) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
  kableExtra::column_spec(2, width = "30em")
```

## Download PDFs for records identified by your search

Pass the results of your search above (`results`) to the `mx_download()` function to download a copy of the PDF for each record. Note: downloaded PDFs are named using the value of the `ID` column in the dataset, which serves as a unique identifier for each record.

```{r, eval = FALSE}

mx_download(results,        # Object returned by mx_search
            "pdf/",         # Directory to save PDFs to 
            create = TRUE)  # Create the directory if it doesn't exist

```

## Further guidance

Please see the *[Building complex search strategies](https://mcguinlu.github.io/medrxivr/articles/building-complex-search-strategies.html)* vignette for extended guidance on developing search strategies for use with `medrxivr`.
