---
title: "Interacting with the medRxiv API"
author: "Luke A McGuinness"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: yes
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{medrxiv-api}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=FALSE, message=FALSE,warning=FALSE}
# Delete when done
library(medrxivr)
library(dplyr)

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

## Background

The [medRxiv API](https://api.biorxiv.org/) provides a direct interface to the medRxiv database. **However, the API does not allow you to perform searches,** instead providing two endpoints that return either all content between two specified dates or all information held on a particular DOI. 

`medrxivr` provides two convience functions for importing the data provided by these endpoints in R: `mx_api_content()` and `mx_api_doi()`. The results of either function can then be passed to `mx_search()` for searching.

### By date range (`mx_api_content()`)

The format of this endpoint is https://api.biorxiv.org/details/medrxiv/[interval]/[cursor] where 'interval' must be two YYYY-MM-DD dates separted by '/'. Where metadata for multiple papers is returned, results are paginated with 100 papers served in a call. The 'cursor' value can be used to iterate through the result. 

`mx_api_content()` automatically moves through the pages for you, capturing all records returned by the endpoint and returning them as an R object. For instance, https://api.biorxiv.org/details/medrxiv/2020-01-01/2020-01-31/0 will output 100 results (if that many remain) within the date range of 2020-01-01 to 2020-01-31 beginning from result 1. To import this into R as a dataframe:

``` {r}
medrxiv_data <- mx_api_content(from.date = "2020-01-01", 
                               to.date = "2020-01-31")
```

### By DOI (`mx_api_doi()`)

https://api.biorxiv.org/details/[server]/[DOI] returns detail for a single manuscript. For instance, https://api.biorxiv.org/details/medrxiv/10.1101/2020.02.25.20021568 will output metadata for the medrxiv paper with DOI 10.1101/2020.02.25.20021568. To import the results from this endpoitn into R as a dataframe:

``` {r}
medrxiv_data <- mx_api_doi(doi = "10.1101/2020.02.25.20021568")
```

## Notes

Both functions contain a `clean` argument with is set to `TRUE` by default. This is to ensure that the datasets returned by the `mx_api_*()` functions can immediately be passed to `mc_search()`. Howevever, there may be occasions where this is not required, and so setting this argument to `FALSE` will return the raw data provided by the API endpoints.
