---
title: "Get started"
author: "Luke A McGuinness"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_document:
    toc: yes
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{medrxivr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=FALSE, message=FALSE,warning=FALSE}
# Delete when done
library(medrxivr)
library(dplyr)

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

## Perform a simple search using a copy of the database from the API

`medrxivr` provides programmatic access to the medRxiv API. However, the API does not allow you to search the database. Instead, you can download a copy of the database yourself via `mx_api_content()`, and then pass the resulting object to the `mx_search()` function for searching (i.e. rather than using the daily snapshot). This can be useful if you wish to document the exact time and data of your extraction, or if the daily snapshot is not updating.

``` {r, eval=FALSE}

medrxiv_data <- mx_api_content()

results <- mx_search(data = medrxiv_data, 
                     query ="dementia")

```

Alternatively, this can be done all in one step using a piped workflow:

``` {r, eval=FALSE}
library(dplyr)

results <- mx_api() %>%
           mx_search(query ="dementia")

```

## Perform a simple search using the daily snapshot of the database

An alternative to the approach detailed above is to search a daily snapshot of the database, taken each morning using the `mx_api_content()` function. Searches performed using this method do not rely on the API (which can become unavilable during peak times) and are usually faster (as it reads data from a CSV rather than having to re-extract it from the API).

``` {r, eval=FALSE}
library(medrxivr)

results <- mx_search(query ="dementia")

```

## Dataset description

The dataset (in this case, `results`) returned by the search function above contains 10 variables: 

```{r, echo = FALSE}

mx_variables <-
  data.frame(
    Variable = c(
         "ID"      ,
         "title"   ,
         "abstract",
         "authors" ,
         "date"    ,
         "category",
         "doi"     ,
         "version" ,
         "author_corresponding",
         "author_corresponding_institution",
         "link_page",
         "link_pdf" ,
         "license"  ,
         "published"
    ),
    Description = c(
      "Unique identifier",
      "Preprint title",
      "Preprint abstract",
      "Author list in the format 'LastName, InitalOfFirstName.' (e.g. McGuinness, L.). Authors are seperated by a semi-colon.",
      "Date the preprint was posted, in the format YYYYMMDD.",
      "On submission, medRxiv asks authors to classify their preprint into one of a set number of subject categories.",
      "Preprint Digital Object Identifier.",
      "Preprint version number. As authors can update their preprint at any time, this indicates which version of a given preprint the record refers to.", 
      "Corresponding authors name.",
      "Corresponding author's institution.",
      "Link to preprint webpage. The \"?versioned=TRUE\" is required, as otherwise, the URL will resolve to the most recent version of the article (assuming there is >1 version available).",
      "Link to preprint PDF. This is used by `mx_download()` to download a copy of the PDF for that preprint.",
      "Preprint license",
      "If the preprint was subsequently published in a peer-reviewed journal, this variable contains the DOI of the published version."
    )
  )


knitr::kable(mx_variables, format = "html") %>%
  kableExtra::kable_styling(full_width = F) %>%
  kableExtra::column_spec(1, bold = T, border_right = T) %>%
  kableExtra::column_spec(2, width = "30em")
```

## Download PDFs for records identified by your search

Pass the results of your search above (`results`) to the `mx_download()` function to download a copy of the PDF for each record. Note: downloaded PDFs are named using the value of the `ID` column in the dataset, which serves as a unique identifier for each record.

```{r, eval = FALSE}

mx_download(results,        # Object returned by mx_search
            "pdf/",         # Directory to save PDFs to 
            create = TRUE)  # Create the directory if it doesn't exist

```


## Further guidance

Please see the *[Building complex search strategies](https://mcguinlu.github.io/medrxivr/articles/building-complex-search-strategies.html)* vignette for extended guidance on developing search strategies for use with `medrxivr`.
